---
title: "Plots"
output: html_notebook
---

This notebook generates all the plots for the Inverse Optimization of Integer Programming Games document

# Adjustment Inverse Optimization

## Knapsack Problem
```{r}
require(tidyverse)
local_kp <- function(filename, type) {
    df = read_csv(filename, show_col_types = FALSE)
    dodge <- position_dodge(width=0.75)

    ggplot(data = df, mapping = aes(y=factor(items), x=avg, group=factor(range), colour=factor(range))) +
        geom_point(position = dodge) + 
        geom_pointrange(aes(xmin=min, xmax=max), position = dodge, size=0.25) +
        labs(caption="Dots indicate the mean running times and lines indicate minimum and maximum running times.",
             y="items",
             x="running time (seconds)",
             colour="range")
}
```


### Payoffs
```{r}
filename <- "results/kp/local/local_inverse_kp-payoffs-30.csv"
type <- "payoff"
local_kp(filename, type)
```
### Weights
```{r}
filename <- "results/kp/local/local_inverse_kp-weights-30.csv"
type <- "weight"
local_kp(filename, type)
```

## Knapsack Packing Game
```{r}
require(tidyverse)
player_labs <- as_labeller(
     c(`2` = "2 players", `3` = "3 players", `4` = "4 players"))
local_kpg <- function(filename, type) {
    df = read_csv(filename, show_col_types = FALSE)
    dodge <- position_dodge(width=0.75)

    ggplot(data = df, mapping = aes(y=factor(items), x=avg, group=factor(range), colour=factor(range))) +
        geom_pointrange(aes(xmin=min, xmax=max), position = dodge, size=0.25) +
        labs(caption="Dots indicate the mean running times and lines indicate minimum and maximum running times.",
             x="running time (seconds)",
             y="items",
             colour="range") +
        facet_wrap(~players, ncol=1, labeller=player_labs)
}
```

### Payoff
```{r}
filename <- "results/kpg/local/local_inverse_kpg-payoffs-30-4-False.csv"
type <- "payoff"
local_kpg(filename, type)
```

### Weights
```{r}
filename <- "results/kpg/local/local_inverse_kpg-weights-30-4-False.csv"
type <- "weight"
local_kpg(filename, type)
```
## Critical Node Game
```{r}
require(tidyverse)

cng_local_phi <- function(type) {
  measurement_labs = as_labeller(c(`a_runtime`="mean runtime", `diff`="mean RAC", `phi`="mean phi change"))

  str <- paste("local_inverse_cng-", type, "-10-[0-9]+-nodes.csv", sep="")
  df <- list.files("results/cng/local", full.names = TRUE, pattern=str, include.dirs = FALSE) %>%
    map_dfr(read_csv, show_col_types = FALSE) %>%
    rename(a_runtime=runtime) %>%
    pivot_longer(c(`a_runtime`, `diff`, `phi`), values_to = "value", names_to = "type")

  
  head(df)
  
  
  ggplot(data=df, aes(x=nodes, y=value, colour=factor(norm), linetype=factor(mit))) +
    geom_line(alpha=0.75) +
    facet_grid(type ~ ., scales="free", labeller=measurement_labs) +
    labs(x="nodes", y="", linetype="eta", colour="gamma") 
}

cng_local_greedy <- function(type) {
  
  if (type == "weights") {
    breaks <- c(50, 100, 150, 200)
  } else if (type == "payoffs") {
    breaks <- c(50, 70, 100)
  }
  
  measurement_labs = as_labeller(c(`a_runtime`="mean runtime", `diff`="mean RAC", `pne`="total PNE", `inf`="inf"))

  str <- paste("local_inverse_cng-", type, "-20-[0-9]+-nodes-greedy.csv", sep="")
  df <- list.files("results/cng/local", full.names = TRUE, pattern=str, include.dirs = FALSE) %>%
    map_dfr(read_csv, show_col_types = FALSE) %>%
    rename(a_runtime=runtime) %>%
    pivot_longer(c(`a_runtime`, `diff`, `inf`), values_to = "value", names_to = "type") 
  
  head(df)
  
  ggplot(data=df, aes(x=nodes, y=value, colour=factor(norm), linetype=factor(mit), group=interaction(norm, mit))) +
    geom_line() +
    facet_grid(type ~ ., scales="free", labeller=measurement_labs) +
    labs(x="nodes", y="", linetype="eta", colour="gamma") +
    scale_x_continuous(breaks=breaks)
}

```
### Payoffs

```{r}
type <- "payoffs"

cng_local_greedy(type)
```

```{r}
type <- "payoffs"

cng_local_phi(type)
```


### Weights
```{r}
type <- "weights"

cng_local_phi(type)
```

```{r}
type <- "weights"

cng_local_greedy(type)
```


# Reconstruction inverse optimization

## Knapsack Problem

```{r}
require(tidyverse)

global_kp <- function(type, labels=waiver(), breaks=waiver()) {
    measurement_labs = as_labeller(c(`error`="mean RAC", `a_runtime`="mean runtime"))
    str <- paste("inverse_kp-", type, "-5-[0-9]+-items.csv", sep="")
    df_fixed <- list.files("results/kp", full.names = TRUE, pattern=str, include.dirs = FALSE) %>%
      map_dfr(read_csv, show_col_types = FALSE) %>%
      rename(a_runtime = runtime) %>%
      pivot_longer(c(`a_runtime`,`error`), names_to="measurement", values_to="value")
    df_fixed$cap <- "fixed"
    
    str <- paste("inverse_kp-", type, "-5-[0-9]+-items-rc.csv", sep="")
    df_random <- list.files("results/kp", full.names = TRUE, pattern=str, include.dirs = FALSE) %>%
      map_dfr(read_csv, show_col_types = FALSE) %>%
      rename(a_runtime = runtime) %>%
      pivot_longer(c(`a_runtime`,`error`), names_to="measurement", values_to="value")
    df_random$cap <- "random"
    
    df <- bind_rows(df_fixed, df_random) %>%
      mutate(std_o = o / n)
      
    
    ggplot(data=df, aes(x=std_o, y=value, colour=factor(n), linetype=cap)) +
      geom_line() +
      facet_grid(measurement ~ ., scales="free", labeller=measurement_labs) +
      labs(x="observations", y="", 
           colour="items", linetype="capacity") +
      scale_x_continuous(labels=labels, breaks=breaks)
    
}
```

### Payoffs
```{r}
type <- "payoffs"
breaks <- c(0.5, 2, 4, 6, 8)
labels <- c("items/2", "2 * items", "4 * items", "6 * items", "8 * items")

global_kp(type, labels, breaks)
```

### Weights


```{r}
type <- "weights"
breaks <- c(1, 2, 3, 4)
labels <- c("items", "2 * items", "3 * items", "4 * items")

global_kp(type, labels, breaks)
```

## Knapsack Packing Game

```{r}
require(tidyverse)

global_kpg <- function(df) {
  measurement_labs = as_labeller(c(`diff`="mean RAC", `a_runtime`="mean runtime"))

  breaks <- c(1, 2, 4, 6, 8)
  labels <- c("items", "2 * items", "4 * items", "6 * items", "8 * items")
  
  df <- df %>%
  rename(a_runtime = runtime) %>%
  pivot_longer(c(`a_runtime`, `diff`), names_to = "measurement", values_to = "value") %>%
  mutate(s_obs = obs / items)

  ggplot(df, aes(x=s_obs, y=value, colour=factor(items), linetype = factor(players))) +
    geom_line() +
    facet_grid(measurement ~ ., scales = "free_y", labeller=measurement_labs) +
    scale_x_continuous(labels = labels, breaks = breaks) +
    labs(x="observations", linetype="players", colour="items", y="")
  
}
```

### Payoffs
```{r}
type <- "payoffs"
str <- paste("inverse_kpg-", type, "-5-[0-9]+-items-False.csv", sep="")
df_false <- list.files("results/kpg", full.names = TRUE, pattern=str, include.dirs = FALSE) %>%
  map_dfr(read_csv, show_col_types = FALSE)

global_kpg(df_false)
```

```{r}
type <- "payoffs"
str <- paste("inverse_kpg-", type, "-5-[0-9]+-items-True.csv", sep="")
df_true <- list.files("results/kpg", full.names = TRUE, pattern=str, include.dirs = FALSE) %>%
  map_dfr(read_csv, show_col_types = FALSE)
global_kpg(df_true)
```


```{r}
type <- "payoffs"
str <- paste("inverse_kpg-", type, "-5-[0-9]+-items-rc.csv", sep="")
df_rc <- list.files("results/kpg", full.names = TRUE, pattern=str, include.dirs = FALSE) %>%
  map_dfr(read_csv, show_col_types = FALSE)

global_kpg(df_rc)
```

### Weights
```{r}
type <- "weights"
str <- paste("inverse_kpg-", type, "-5-[0-9]+-items.csv", sep="")
df_false <- list.files("results/kpg", full.names = TRUE, pattern=str, include.dirs = FALSE) %>%
  map_dfr(read_csv, show_col_types = FALSE)

global_kpg(df_false)
```

```{r}
type <- "weights"
str <- paste("inverse_kpg-", type, "-5-[0-9]+-items-rc.csv", sep="")
df_rc <- list.files("results/kpg", full.names = TRUE, pattern=str, include.dirs = FALSE) %>%
  map_dfr(read_csv, show_col_types = FALSE)

global_kpg(df_rc)
```

